Investigation of Limited Detection Schemes for Light Scattering of Optically Trapped Asymmetric Particles

### 2022-11-29 Manuscript_rev1.tex
Add files via upload

We use the Brownian OT package developed by Fung~\textit{et~al}.
\cite{Vigilante2020Brownian_OT} to simulate the motion of a asymmetric
dimer within an optical trap.  Brownian OT combines MSTM
\cite{Mishchenko1996MSTM} and ``Optical Tweezer Toolbox''
(\textit{ott}) \cite{Lenton2020} to simulate the motion of arbitrary
shaped sphere clusters.  We simulated the motion of silica dimer
trapped in a $5$\,mW Gaussian beam; the dimer was comprised of two
spheres with radii $1\,{\rm \mu m}$ and $ 0.5\,{\rm \mu m}$,
respectively.  We ran our simulation over the span of 10 seconds, with
Brownian OT calculating the dimer's orientation and position every
$1 \ ms$.

@@

Using our simulation from Section~\ref{sec:brownian} we calculated the instantaneous signal from our dimer at each time step using MSTM.  We applied Eq.~\eqref{eq:bayes} --- covered in Section~\ref{sec:Bayes} --- and the reference orientation with the highest probability is taken as our estimation of the dimer's instantaneous orientation. To visualise our model's performance  we plotted the radial distance between our estimation $\hat{\bf n}_{est}$ of the orientation and the dimer's \emph{actual} instantaneous orientation $\hat{\bf s}$ versus time. For comparison, we also plotted the radial distance between the closest reference orientation, denoted $\hat{\bf n}_{best}$, and the dimer's instantaneous orientation. If we assume our prior of the reference orientations $p(\hat{\bf n}_\alpha)$ to be uniform the performance is poor, as seen in \ref{fig:uniform}.

@@

A key assumption of Eq.~\eqref{eq:conditional} is that we assume our
detected light signal will inherently have some degree of noise. This
is the central premise that allows us to form
Eq.~\eqref{eq:conditional}, understanding the limits of acceptable
signal error is necessary for implementing this to experimental work.
To this end we ran our model while varying the value of $\epsilon$.
\figurename{ 3} shows the performance of the method with a selection
of angles $15^{\circ}$, $55^{\circ}$, and $90^{\circ}$ and $\beta$ set
to $1$.  The dotted line indicates the minimum radian distance
($0.137$ radians) between two neighbouring reference orientations, if
we are under this line then we know our model is just off from
selecting the correct orientation:

@@

As can be seen from Figure~\ref{fig:epsilon}, there is seemingly a
sweet spot for the signal error; with a $5$\% error giving an
inaccurate estimation, and with a $25$\% error giving an alright
estimation but with sudden shifts away from the ideal result. The
reason why our low error estimation performed so poorly is that the
minimum difference between our values of $y_k$ is larger than our
signal error.  As such the model could not distinguish between
different reference orientations and was essentially just picking
options at random.  This minimum difference determined by our choice of
angles and sets a lower limit of how accurate our signals can be.  In
the future we hope to look at increasing the number of reference
orientations to see what the true lower bound is.

The latter issue of a high signal error can be addressed somewhat by
adjusting our value of $\beta$ to flatten our probability
distribution. We repeated our model estimation at $25\%$ at different
values of $\beta$ to see the upper limit we could improve our result
to.

@@

As shown in Figure~\ref{fig:beta}, eventually $\beta$ begins to over
correct our estimate to the extent that we are a full radian away from
the correct result.  The exact value of $\beta$ that will optimise our
performance varies for each choice of angle, therefore we can use it
as variable for finely tuning our results to suit our choice of angles
and our signal error.  In future, we want to also investigate the
possibility of extending our prior $p(\hat{\bf n})$ so we account for not
just the change in orientation after one time step but after 2 or 3
time steps to investigate if we can investigate the auto correlation
of our dimer's motion.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
\subsection{Parameter Optimisation Results}
\label{sec:ultranest_res}

@@

Figure~\ref{fig:corner} is the resulting corner plot from our
ultranest sampler, darker areas indicate a choice of angles where the
model performed better where as lighter areas are where the model did
poorer.  Overall from the corner plot provided, it is clear that there
is no direct correlation between our method's performance and the
choice of detection angle. While the choice of angles does not provide
a direct improvement in our estimation it does determine how finely we
can estimate the orientation, for choices of angles that are close
together the minimum spacing between our signals is so small that we
cannot achieve any greater accuracy than dividing the orientation
space into $n_{\rm ref}=30$ reference orientations.  We hope to
develop our method further in the future by being able to determine
the maximum accuracy given that we know the signal error of our
measurements.

@@

>>>>

We use the Brownian OT package developed by Fung~\textit{et~al}.
\cite{Vigilante2020Brownian_OT} to simulate the motion of a asymmetric
dimer within an optical trap.  Brownian OT combines MSTM
\cite{Mishchenko1996MSTM} and ``Optical Tweezer Toolbox''
(\textit{ott}) \cite{Lenton2020} to simulate the motion of arbitrary
shaped sphere clusters.  We simulated the motion of silica dimer
trapped in a $5$ mW Gaussian beam; the dimer was comprised of two
spheres with radii $1\,{\rm \mu m}$ and $ 0.5\,{\rm \mu m}$,
respectively.  We ran our simulation over the span of 10 seconds, with
Brownian OT calculating the dimer's orientation and position every
$1 \ ms$.

@@

Using our simulation from Section~\ref{sec:brownian} we calculated the instantaneous signal from our dimer at each time step using MSTM.  We applied Eq.~\eqref{eq:bayes} --- covered in Section~\ref{sec:Bayes} --- and the reference orientation with the highest probability is taken as our estimation of the dimer's instantaneous orientation. To visualise our model's performance  we plotted the radial distance between our estimation $\hat{\bf n}_{est}$ of the orientation and the dimer's \emph{actual} instantaneous orientation $\hat{\bf s}$ versus time. For comparison, we also plotted the radial distance between the closest reference orientation, denoted $\hat{\bf n}_{best}$, and the dimer's instantaneous orientation. The dotted line indicates the maximum radian distance ($0.896$ radians) between two neighbouring reference orientations, if we are under this line then we know our estimate and the best result are beside one another. If we assume our prior of the reference orientations $p(\hat{\bf n}_\alpha)$ to be uniform the performance is poor, as seen in \ref{fig:uniform}.

@@

A key assumption of Eq.~\eqref{eq:conditional} is that we assume our
detected light signal will inherently have some degree of noise. This
is the central premise that allows us to form
Eq.~\eqref{eq:conditional}, understanding the limits of acceptable
signal error is necessary for implementing this to experimental work.
To this end we ran our model while varying the value of $\epsilon$.
\figurename{ 3} shows the performance of the method with a selection
of angles $15^{\circ}$, $55^{\circ}$, and $90^{\circ}$ and $\beta$ set
to $1$:

@@

As can be seen from Figure~\ref{fig:epsilon}, there is a
sweet spot for the signal error; with a $5$\% error giving an
inaccurate estimation, and with a $25$\% error giving an alright
estimation but with sudden shifts away from the ideal result. The
reason why our low error estimation performed so poorly is that the
minimum difference between our values of $y_k$ is larger than our
signal error. As such the model could not distinguish between
different reference orientations and was essentially just picking
options at random. This minimum difference determined by our choice of
angles and sets a lower limit of how accurate our signals can be. In
the future we hope to look at increasing the number of reference
orientations to see what the true lower bound is.

The latter issue of a high signal error can be addressed somewhat byadjusting our value of $\beta$ to flatten our probability distribution. We repeated our model estimation at $25\%$ at different values of $\beta$ to see the upper limit we could improve our result to.

@@

As shown in Figure~\ref{fig:beta}, eventually $\beta$ begins to over correct our estimate to the extent that we are a full radian away from the correct result.  The exact value of $\beta$ that will optimise our performance varies for each choice of angle, therefore we can use it as variable for finely tuning our results to suit our choice of angles and our signal error.  In future, we want to also investigate the possibility of extending our prior $p(\hat{\bf n})$ so we account for not just the change in orientation after one time step but after 2 or 3 time steps to investigate the auto correlation function of our dimer's motion.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Parameter Optimisation Results}
\label{sec:ultranest_res}

@@

Figure~\ref{fig:corner} is the resulting corner plot from our ultranest sampler, darker areas indicate a choice of angles where the model performed better where as lighter areas are where the model did poorer. Overall from the corner plot provided, it is clear that there is no direct correlation between our method's estimation of orientation and the
choice of detection angle. While the choice of angles does not provide a direct improvement in our estimation it does determine how finely we can estimate the orientation, for choices of angles that are close together the minimum spacing between our signals is so small that we cannot achieve any greater accuracy than dividing the orientation space into $n_{\rm ref}=30$ reference orientations.  We hope to develop our method further in the future by being able to determine the maximum accuracy given that we know the signal error of our measurements.

@@

This result only indicates that orientation is not a characteristic that is angularly biased in its scattering. It might well be that for other characteristics, such as size or shape, the choice of detection angles may have a more direct impact on our model's performance.
